%!TEX program = xelatex

\documentclass[a4paper, openany, oneside]{memoir}
\input{../../../../includes/preamble.tex}
\addbibresource{../../../../includes/bibliography.bib}

\begin{document}

\section{Energy detection}

\begin{figure}[H]
\centering
\begin{tikzpicture}
\node at (-5,3) {$x(t)$};
\node at (4.3,3) {$\mathcal{H}_0 \text{ or } \mathcal{H}_1$};
\draw [>=latex, ->] (-3,3) -- (-2.5,3);
\draw (-4,3.5) rectangle (-3,2.5) node[pos=.5]{$H(f)$};
\draw [>=latex, ->] (-4.5,3) -- (-4,3);
\draw (-2.5,3.5) rectangle (-1.5,2.5) node[pos=.5]{ADC};
\draw [>=latex, ->] (-1.5,3) -- (-1,3);
\draw (-1,3.5) rectangle (0,2.5) node[pos=.5]{$|\cdot|^2$};
\draw [>=latex, ->] (0,3) -- (0.5,3);
\draw (0.5,3.5) rectangle (1.5,2.5) node[pos=.5]{$\sum$};
\draw [>=latex, ->] (1.5,3) -- (2,3); 
\draw (2,3.5) rectangle (3,2.5) node[pos=.5]{$_<^ > \gamma$};
\draw [>=latex, ->] (3,3) -- (3.5,3);
\end{tikzpicture}
\caption{Conventional Energy Detector}\label{tkz:conv_ed}
\end{figure}
A standard digital energy detector is a detector that consists of a lowpass filter $H(f)$ that filters the analog input signal $x(t)$ such
that only the frequency band of interest remains. This filtered signal is then converted to a digital signal $x[n]$ by an analog-to-digital converter (ADC). The detector estimates the energy $\Lambda$ of the signal during a period of $N$ samples as follows
\begin{align}\label{eq:test_ed}
	\Lambda &= \sum_{n=0}^{N-1} |x[n]|^2.
\end{align}
This estimate is then compared to a threshold $\gamma$ to decide whether a signal other than noise is present in $x[n]$. That is, $\Lambda$ serves as test statistic for the binary hypothesis problem
\begin{align*}
	\begin{cases}
		\mathcal{H}_0 & \text{if } \Lambda < \gamma \\
		\mathcal{H}_1 & \text{if } \Lambda > \gamma.
	\end{cases}
\end{align*}
The threshold $\gamma$ depends on the noise power $\sigma_n^2$  and the desired false alarm probability $p_{fa}$: the probability that the detector decides that hypothesis 2 is true, while hypothesis 1 is the true hypothesis. The derivation of $\gamma$ (see Appendix ...) gives the following result
\begin{align*}
\gamma = \left[Q^{-1}(p_{fa})\sqrt{N} + N\right]2\sigma_n^2
\end{align*}
where $Q^{-1}$ denotes the the inverse tail probability function of the standard normal distribution and $p_{fa}$ is the desired false alarm probability.
% As can be seen from  \cref{eq:test_ed} the test statistic used by the conventional energy detector does not take into account that the signal to be detected resides in a certain frequency band. Therefore it is necessary that the input signal $x[n]$ is filtered before $\Lambda$ is computed.
\begin{figure}[H]
\centering
\begin{tikzpicture}
\node at (-2,3) {$r_x[n]$};
\node at (4.3,3) {$\mathcal{H}_0 \text{ or } \mathcal{H}_1$};
\draw [>=latex, ->] (-1.5,3) -- (-1,3);
\draw (-1,3.5) rectangle (0,2.5) node[pos=.5]{FFT};
\draw [>=latex, ->] (0,3) -- (0.5,3);
\draw (0.5,3.5) rectangle (1.5,2.5) node[pos=.5]{$\sum$};
\draw [>=latex, ->] (1.5,3) -- (2,3); 
\draw (2,3.5) rectangle (3,2.5) node[pos=.5]{$_<^ > \gamma$};
\draw [>=latex, ->] (3,3) -- (3.5,3);
\end{tikzpicture}
\caption{Energy detector in frequency domain}
\label{tkz:ed_psd}
\end{figure}

As can be seen from \cref{eq:test_ed} the test statistic $\Lambda$ depends on the signal itself, not on the autocorrelation or the power spectral density which serves as input of our detector. We will now establish this relation by modifying the test statistic $\Lambda$.
Let 
\begin{align*}
\Lambda' &= \frac{\Lambda}{N}\\
	&= \frac{\sum_{n=0}^{N-1} |x[n]|^2}{N},
\end{align*}
then $\Lambda'$ is an estimate of the average power $E\left[|x[n]|^2\right]$ of the signal $x$. We can use $\Lambda'$ as test statistic by using a modified threshold $\gamma' = \frac{\gamma}{N}$. To relate the power spectral density, which serves as input of our detector, to $\Lambda'$  we notice that by definition the integral over the power spectral density equals the expected average power:
\begin{align}\label{eq:average_power_psd}
E\left[\left|x[n]\right|^2\right] = \frac{1}{2\pi} \int_{-\pi}^{\pi}\mathcal{P}_x(\omega) \text{d}\omega.
\end{align}
Furthermore, by the Wiener-Khinchin theorem we have, if $x[n]$ is wide-sense stationary, that
\begin{align}\label{eq:wiener_psd}
	\mathcal{P}_x(\omega) &= \mathcal{F}(r_x[n]) \\
	&= \sum_{n=-\infty}^{\infty} r_x[n] \exp [2\pi j\omega],
\end{align}
where the $\mathcal{F}(\cdot)$ denotes the Discrete Time Fourier Transform. 
By combining \cref{eq:average_power_psd} and \cref{eq:wiener_psd} we can also relate the autocorrelation function to the test statistic $\Lambda'$. A energy detector using the test statistic is depicted in \cref{tkz:ed_psd}\footnote{it is assumed that $r_x[n]$ is based on an appropriate filtered signal}. A discrete power spectral density is estimated by applying the Fast Fourier Transform to $r_x[n]$. By summating over the obtained discrete power spectral density, an estimate of the average power is obtained. This estimate may then be compared with the threshold $\gamma'$.  
\begin{figure}[H]
\centering
\begin{tikzpicture}
\node at (-6.5,2.5) {$r_x[n]$};

\draw [>=latex, ->] (-6,2.5) -- (-5.5,2.5);
\draw (-5.5,3) rectangle (-4.5,2) node[pos=.5]{$\mathcal{F}$};

\draw [>=latex, ->] (-4.5,2.5) -- (-3.5,2.5);
\draw (-3.5,3) rectangle (-2.5,2) node[pos=.5]{$\int P_x$};

\draw [>=latex, ->] (-2.5,2.5) -- (-2,2.5);
\draw (-2,3) rectangle (-1,2) node[pos=.5]{$_<^ > \gamma$};

\draw [>=latex, ->] (-1,2.5) -- (-0.5,2.5);
\node at (0.3,2.5) {$\mathcal{H}_0 \text{ or } \mathcal{H}_1$};


\draw [>=latex, ->] (-4,1) -- (-3.5,1);
\draw (-3.5,1.5) rectangle (-2.5,0.5) node[pos=.5]{$\int P_x$};

\draw [>=latex, ->] (-2.5,1) -- (-2,1);
\draw (-2,1.5) rectangle (-1,0.5) node[pos=.5]{$_<^ > \gamma$};

\draw [>=latex, ->] (-1,1) -- (-0.5,1);
\node at (0.3,1) {$\mathcal{H}_0 \text{ or } \mathcal{H}_1$};


\draw [>=latex, ->] (-4,-1) -- (-3.5,-1);
\draw (-3.5,-0.5) rectangle (-2.5,-1.5) node[pos=.5]{$\int P_x$};

\draw [>=latex, ->] (-2.5,-1) -- (-2,-1);
\draw (-2,-0.5) rectangle (-1,-1.5) node[pos=.5]{$_<^ > \gamma$};

\draw [>=latex, ->] (-1,-1)-- (-0.5,-1);
\node at (0.3,-1) {$\mathcal{H}_0 \text{ or } \mathcal{H}_1$};

\draw (-4,2.5) -- (-4,-1);


\node at (-3,0.11) {\vdots};
\node at (-1.5,0.11) {\vdots};
\node at (0.3,0.11) {\vdots};

\end{tikzpicture}
\caption{Energy detection, multiple frequency bands}\label{tkz:my_ed}
\end{figure}
The implementations of the energy detector proposed up until now do not allow for detection in multiple frequency bands. We will now propose a such an energy detector, which is depicted in \cref{tkz:my_ed}. By integrating over a specific band $W$ in the PSD an estimate of the average power in that band is obtained. This estimate is then compared to a threshold $\gamma''$ to determine the presence of a signal in that band.

Notice that if $x[n]$ contains only white noise, then its autocorrelation function equals a delta function: $r_x[n] = \sigma_n^2\delta[n]$, with $\sigma_n^2$ the noise power. Therefore the power spectral density of $x[n]$, denoted by $\mathcal{P}(\omega)$ equals  
 \begin{align*}
 \mathcal{P}_x(\omega) &= \mathcal{F}(r_x[n])\\
  &= \sigma_n^2.
 \end{align*} The power spectral density is constant. If we want to detect the presence of a signal in a certain frequency band $W$, we can make use of this characteristic. Let
 \begin{align*}
 \Lambda'' &= \int_W \mathcal{P}(\omega) \text{d}\omega
 \end{align*}
denote the test statistic to detect a signal in the frequency band $W$.
 If we integrate the power spectral density of white noise over $W$ we obtain an average power of  $\frac{W}{2\pi} \sigma_n^2$. Therefore if we are to use $\Lambda''$ as test statistic, we have to use the modified threshold $\gamma'' = \frac{W}{2\pi} \gamma'$. 

 If the power spectral density is estimated by a Fast Fourier Transform on $r_x[n]$, then an estimate of $\Lambda''$ can be obtained by summating
 the estimate over the desired frequency band. This would in principle allow for per frequency detection. This detector, however, is flawed: note that by increasing the bandwidth one is summating over, one decreases the variance of the test statistic. Or the other way around: by decreasing the bandwidth to just one sample of the discrete power spectral density one increases the variance of the test statistic. Increasing the variance of the test statistic means that we cannot use $\gamma''$ to achieve our desired $p_{fa}$. 
 
Furthermore, note that this detector also depends on the amount of samples $N$ that were used to calculate $\Lambda$. However, this poses a problem if the detector uses the estimated autocorrelation of the reconstructor: what is $N$?

In signal processing the autocorrelation function $r_x[n]$ is usually estimated by 
\begin{equation}\label{eq:acf_est}
r_x[n] = \frac{1}{N-|n|}\sum_{m=\max(0,n)}^{N-1+\min(0,n)} x[m]\overline{x}[m-n]
\end{equation}
By \cref{eq:acf_est} we have that $r_x[0] = \sum_{n=0}^{N-1} |x[n]|^2 = \Lambda$. That is, $N$ should be the amount of samples needed to estimate $r_x[0]$ in case that \cref{eq:acf_est} is used. 
The reconstructor does not use \cref{eq:acf_est}, instead it combines samples from multiple cosets, which obscures what the value of $N$ should be. 
% \todo{Derive threshold based on distribution of $r_x[0]$}

% \subsection{Noise variance}
% As indicated, knowledge of the noise variance is necessary for the energy detector to work. In practical situations this noise variance may be estimated from a reference measurement in an empty frequency band. 
\subsection{Energy detection with knowledge of the reconstructor}  
\begin{figure}[H]
\centering
\begin{tikzpicture}

\node at (-3,4) {$r_x[n]$};

\draw [>=latex, ->] (-2.5,4) -- (-2,4);

\draw (-2,4.5) rectangle (-1,3.5) node[pos=.5]{FFT};

\draw [>=latex, ->] (-1,4) -- (-0.5,4);
\node at (0.3,4) {$PSD[k]$};

\node at (-3.2,2.5) {$PSD[k]$};

\draw [>=latex, ->] (-2.5,2.5) -- (-2,2.5);

\draw (-2,3) rectangle (-1,2) node[pos=.5]{$_<^ > \gamma_k$};

\draw [>=latex, ->] (-1,2.5) -- (-0.5,2.5);
\node at (0.3,2.5) {$\mathcal{H}_0 \text{ or } \mathcal{H}_1$};

\end{tikzpicture}
\caption{Energy detection with knowledge of the reconstructor}\label{tkz:ed_ari_overview}
\end{figure}
The problem with the multi-band energy detector as described above is that the parameter $N$ is not straightforward to determine. Furthermore, the threshold $\gamma''$ will not yield the correct false alarm probability. This section will be concerned with analyzing the energy detector as proposed in \cite{ariananda2012compressive}. This energy detector calculates an estimate of the power spectral density by applying a Fast Fourier transform on an estimate of the autocorrelation $r_x[n]$. It then performs an element-wise comparison on the power spectral density with a frequency dependent threshold. This detector is depicted in \cref{tkz:ed_ari_overview}.

Let $\vec{s}_x \in \mathbb{R}^{2LN+1}$ denote the discrete power spectral density vector obtained by applying the $(2LN+1)$ point Discrete Fourier Transform to $\vec{r}_x$. 

The vector $\vec{s}_x$ is then given by
\begin{align}
\vec{s}_x &= F_{(2NL+1)}\vec{r}_x
\end{align}
where $F_{(2NL+1)}$ denotes the $(2LN+1)\times (2LN+1)$ DFT matrix. 

To determine the threshold $\gamma_{k}$ for each element of the $\vec{s}_x$, the signal $x[n]$ is assumed to contain only white noise. The distribution of the elements of the reconstructed power spectral density can then be approximated as a gaussian distribution \footnote{For the interested reader, see the Appendix \textbf{TODO} for a derivation}, which we will denote as $(\vec{s}_x)_k \sim \mathcal{N}(\mu_k, \sigma_k^2)$.
Given $\mu_k$ and $\sigma^2_k$, the threshold for each frequency $\omega$ given a false alarm probability $p_{fa}$ can be calculated as by noting that:
\begin{align}\label{eq:pfa_ari}
p_{fa} &= P\left(E(s_k) > \gamma_k \big| \mathcal{H}_0\right) \\
&= P\left(0 > \frac{\gamma_k -E(s_k)}{\Var(s_k)} \big| \mathcal{H}_0\right) \nonumber \\
&= Q(\frac{\gamma_k -E(s_k)}{\Var(s_k)}) \nonumber.
\end{align}
The threshold $\gamma_k$ can then be obtained by solving \cref{eq:pfa_ari} for $\gamma_k$
\begin{align*}
\gamma_k &= Q^{-1}(p_{fa})\sigma_k + \mu_k.
\end{align*}
To obtain $\mu_k = E\left((\vec{s}_x)_k\right)$ notice that
\begin{align}\label{eq:exp_sx}
E\left(\vec{s}_x\right) &= \mat{F}\mat{R}^{\dagger}E\left(\vec{r}_y\right).
\end{align} where the elements of $\vec{r}_y$ are given by 
\begin{align}\label{eq:exp_ry}
\vec{r}_{y_i, y_j}[k] &= (c_{i,j} \ast r_x)[mN]& \text{\cref{eq:cij-rx}} \\
&= c_{i,j}[0]\delta[k]. \nonumber
\end{align}
Therefore $\mu_k$ can be obtained by evaluating the $k^{th}$ element of $E\left(\vec{s}_x\right)$ using \cref{eq:exp_sx} and \cref{eq:exp_ry}.
Now that we have found $\mu_k$ we turn to the problem of finding $\sigma^2_k$. Let the covariance matrix of a vector $\vec{a}$ be defined as
\begin{align}\label{eq:cov_mat}
\mat{C}_a &= E(\vec{a}\vec{a}^H) - E(\vec{a})E(\vec{a}^H),
\end{align}
then element $C_{ij}$ is given by
\begin{align}\label{eq:elem_cov_mat}
C_{a_{ij}}&= \begin{cases}
\Var(a_i, a_i) & \text{if } i=j\\
\Cov (a_i, a_j) & \text{if } i\neq j.
\end{cases}
\end{align}
Notice that the diagonal elements of a covariance matrix equal the variances of its corresponding vector. We will therefore compute the covariance matrix of $\vec{s}_x$ to obtain $\sigma_k^2$. Let the covariance matrix of $\vec{s}_x$ be denote by $\mat{C}_s$, then
\begin{align*}
\mat{C}_{s} &= E\left[\vec{s}_x\vec{s}_x^H\right] - E\left[\vec{s}\right]E\left[\vec{s}^H\right] \\
&= E\left[\left(\mat{F} \mat{R}^{\dagger}\vec{r}_y\right) \left( \mat{F}\mat{R}^{\dagger}\vec{r}_y\right)^H\right] - E\left[\mat{F}\mat{R}^{\dagger}\vec{r}_y\right]E\left[\left(\mat{F}\mat{R}^{\dagger}\vec{r}_y\right)^H\right] \\
&= \mat{F}\mat{R}^{\dagger} E\left[ \vec{r}_y\vec{r}_y^H\right]  \mat{R}^{\dagger H}\mat{F}^H -  \mat{F}\mat{R}^{\dagger} E\left[ \vec{r}_y\right] E\left[\vec{r}_y^H\right]   \mat{R}^{\dagger H}\mat{F}^H \\
&= \mat{F}\mat{R}^{\dagger} \mat{C}_{r_y} \mat{R}^{\dagger H}\mat{F}^H
\end{align*}
where $\mat{C}_{r_y}$ denotes the covariance matrix of $\vec{r}_y$. The elements of $\mat{C}_{r_y}$ are given by\cite{ariananda2012compressive}
\begin{align}\label{eq:elem_cov_ry}
	\Cov(r_{y_{rs}}[t], r_{y_{uv}}[w]) &= \frac{\sigma_n^4 c_{ru}[0]\conj{c}_{sv}[0]\delta[w-t]}{K-|t|}
\end{align}

% \begin{figure}[H]
% \centering
% \begin{tikzpicture}

% \draw [fill=lightgray] (-2,0) rectangle (1,-1);
% \draw (1,3) rectangle (3,-1);
% \draw [fill=cyan, opacity=0.2] (1,3) rectangle (3,-1);
% \draw [fill=lightgray](3,0) rectangle (9,-1);


% \draw [>=latex,<->] (-2.1,-1) -- (-2.1,0);
% \node at (-2.4,-.5) {$\sigma^2_n$};

% \draw [red] (-2,.1) -- (9.2,.1);

% \draw [>=latex,<->] (9.2,-1) -- (9.2,.1);
% \node at (9.4,-.4 ) {$\gamma$};

% \node at (-2,-1.5) {0 rad/s};
% \node at (9,-1.5) {$2\pi$ rad/s};
% \end{tikzpicture}
% \caption{Energy detection with power spectral density}\label{tkz:ed_ari}
% \end{figure}

\section{Covariance absolute value method}
The covariance absolute value detection method as introduced in \cite{zheng2009spectrum} does \emph{not} depend on the noise power $\sigma_n^2$. Its test statistic is based on the structure of the autocorrelation function $r_x[n]$. 

\begin{figure}[H]
\centering
\begin{tikzpicture}

\node at (-4,4.5) {$r_x[n]$};

\draw [>=latex, ->] (-3.5,4.5) -- (-3,4.5);

\draw (-3,5) rectangle (-2,4) node[pos=.5]{};
\draw [>=latex, ->] (-2,4.5) -- (-1.5,4.5);

\draw (-1.5,5) rectangle (-0.5,4) node[pos=.5]{$|\cdot|$};
\draw [>=latex, ->] (-0.5,4.5) -- (0.5,4.5);

\draw (2.5,5) rectangle (3.5,4) node[pos=.5]{$_<^ > \gamma$};
\draw [>=latex, ->] (3.5,4.5) -- (4,4.5);

\draw (0.5,5) rectangle (1.5,4) node[pos=.5]{$\sum$};
\draw [>=latex, ->] (1.5,4.5) -- (2.5,4.5);

\draw (0.5,3.5) rectangle (1.5,2.5) node[pos=.5]{Tr($\cdot$)};

\node at (4.8,4.5) {$\mathcal{H}_0 \text{ or } \mathcal{H}_1$};

\draw (0,4.5) -- (0,3);
\draw (2,4.5) -- (2,3);
\draw (2,3) -- (1.5,3);
\draw [>=latex,->] (0,3) -- (0.5,3);

\draw (-2.6,4.3) -- (-2.7,4.4);

\draw (-2.45,4.3) -- (-2.7,4.55);
\draw (-2.3,4.3) -- (-2.7,4.7);
\draw (-2.3,4.45) -- (-2.55,4.7);

\draw (-2.3,4.6) -- (-2.4,4.7);

\draw (-2.8,4.8) -- (-2.8,4.2);
\draw (-2.8,4.8) -- (-2.7,4.8);
\draw (-2.8,4.2) -- (-2.7,4.2);

\draw (-2.2,4.8) -- (-2.2,4.2);
\draw (-2.2,4.2) -- (-2.3,4.2);
\draw (-2.2,4.8) -- (-2.3,4.8);


\end{tikzpicture}
\caption{CAV detector}\label{tkz:cav}
\end{figure}

The process of the CAV detector as depicted  in \cref{tkz:cav} consist out of 5 steps:
\begin{enumerate}
	\item Calculate the $L\times L$ symmetric toeplitz matrix $\mat{C}$ using the first $L$ samples of $r_x[n]$ as the first column.
	\item Take the absolute value of all elements of this toeplitz matrix
	\item Calculate $T_1 = \sum_{n=1}^{L-1}\sum_{m=1}^{L-1} C_{nm}$
	\item Calculate $T_2 = \text{Tr}(\mat{C})$
	\item Compare $\frac{T1}{T2}$ to a threshold $\gamma$. In case that $\frac{T_1}{T_2} > \gamma$ it is decided that $\mathcal{H}_1$ is true, otherwise $\mathcal{H}_0$ is regarded as the true hypothesis. 
\end{enumerate}

\subsection{Explanation}
Let $L$ samples of the signal $x[n]$ be collected in the vector $\vec{x} = \left[x[n], x[n+1], \ldots, x[n+L]\right]^T$. 
Furthermore let $\mat{C} = E\left(\left(\vec{x} - \mu \right)\left(\vec{x} - \mu \right)^H\right)$ denote the covariance of $\vec{x}$ with $\mu = E(\vec{x})$.

In the case that $E\left(\vec{x}\right)=0$, like for noise or most communication signals, then $\mat{C}$ can be simplified to

\begin{align*}
\mat{C}_x &= E\left(\vec{x}\vec{x}^T\right) \\
&= \begin{bmatrix} 
E\left(x[n][n]\right) & E\left(x[n][n+1]\right) & \ldots & E\left(x[n][n+L-1]\right) \\
E\left(x[n+1][n]\right) & E\left(x[n+1][n+1]\right) & \ldots & E\left(x[n+1][n+L-1]\right) \\
\vdots & \vdots & \ddots & \vdots \\
E\left(x[n+L-1][n]\right) & E\left(x[n+L-1][n+1]\right) & \ldots & E\left(x[n+L-1][n+L-1]\right) \\
\end{bmatrix}.
\end{align*}
Under the assumption that $x[n]$ is a wide-sense stationary signal, we can simplify $\mat{C}$ even further:
\begin{align*}
\mat{C}&= E\left[\vec{x}\vec{x}^T\right] \\
&= \begin{bmatrix} 
r_x[0] & r_x[1] & \ldots & r_x[L-1] \\
r_x[1] & r_x[0] & \ldots & r_x[L-2] \\
\vdots & \vdots & \ddots & \vdots \\
r_x[L-1] & r_x[L-2] & \ldots & r_x[0] \\
\end{bmatrix}.
\end{align*}
Note how $\mat{C}$ is symmetric and Toeplitz: this is the first block in \cref{tkz:cav}. As  the autocorrelation function of white noise is a delta function, it means that  if $x[n]$ is white noise with variance $\sigma_n^2$ then $\mat{C}_x = \sigma_n^2\mat{I}$.
If the signal $x[n]$ is not equal to noise, then its autocorrelation function is not equal to a delta function which results in $\mat{C}$ having non-zero off diagonal elements.

Covariance absolute value method detection uses a measure of this ``diagonality'' of $\mat{C}$ as test statistic $\Lambda$.
This measure $\Lambda$ is defined as
\begin{align}\label{eq:cav_statistic}
\Lambda &= \frac{T_1}{T_2} \nonumber \\
&=\frac{\sum_{n=1}^{L} \sum_{m=1}^L \left|\mat{C}_{nm}\right|}{\sum_{k=1}^L |\mat{C}_{kk}}
\end{align} 

with $T_1 = \frac{\sum_{n=1}^{L} \sum_{m=1}^L \left|\mat{C}_{nm}\right|}{L}$ and
$T_2 = \frac{\sum_{k=1}^L |\mat{C}_{kk}}{L}$.
This test statistic can be computed by first taking the absolute value of $\mat{C}$. This is then followed by summing all the elements of the resulting matrix (forming the numerator in \cref{eq:cav_statistic}) and computing the trace (the denominator in \cref{tkz:conv_ed}) of that matrix. Upon diving those two results one obtains the test statistic $\Lambda$. This process is depicted in \cref{tkz:cav}.

In practice one estimates the matrix $\mat{C}$ by using a limited amount of samples $N$ to estimate $r_x[n]$. The threshold given a desired false alarm probability
$p_{fa}$ is derived in \cite{zheng2009spectrum} to be

\begin{align*}
\gamma &= \frac{\left(1+(L-1)\sqrt{\frac{2}{N\pi}}\right)}{1-Q^{-1}(p_{fa})\sqrt{\frac{2}{N}}}.
\end{align*} 

As with the conventional energy detector, it is not trivial how the reconstructor influences the parameter $N$ .

\subsection{Adjusting the threshold}

In \cite{zheng2009spectrum} it is assumed that for large $N$ the distribution of $T_1$ and $T_2$ approach gaussian distributions. Given a fixed false alarm probability, the threshold $\gamma$ is derived under the hypothesis $\mathcal{H}_0$. The following should hold

\begin{align*}
p_{fa} &\approx P\left(\frac{T_1}{T_2} > \gamma \big | \mathcal{H}_0\right) \\
&= P\left(T_2 < \frac{T_1}{\gamma} \big | \mathcal{H}_0\right)
\end{align*}

Under $\mathcal{H}_0$, the distribution of $T_2 = r_x[0]$ is approximated by a gaussian. We can therefore derive the
threshold $\gamma$ by noting that.

\begin{align*}
p_{fa} &= P\left(\frac{\frac{E\left(T_1\right)}{\gamma} - E\left(T_2\right) }{\sqrt{\text{Var}(T_2)}}\right)\\
&= 1-Q\left(\frac{\frac{E\left(T_1\right)}{\gamma} - E\left(T_2\right) }{\sqrt{\text{Var}(T_2)}}\right) 
\end{align*}

To solve for $\gamma$ we have to determine $E\left(T_1\right)$, $E\left(T_2\right)$ and $\Var(T_2)$. It is at this point that we cannot use the expressions from \cite{zheng2009spectrum} as they assume that $r_x[m]$ is estimated by the sample autocorrelation function. 

Let $\vec{\hat{r}_x} = \left[\hat{r}_x[-LN], \hat{r}_x[-LN+1] , \ldots, \hat{r}_x[LN]\right]$ denote the vector containing the, by the reconstructor, estimated elements of $r_x[m]$. Then 

\begin{align*}
E(\vec{\hat{r}}_x) &= \mat{R}^{\dagger}E(\vec{r}_y)
\end{align*}

contains $r_x[m]$ for $-LN \leq m \leq LN$. Notice that this vector contains $r_x[0] = E(T_2)$ and can be used to construct $E(\mat{C})$ (and therefore can be used to determine $E(T_1)$).

To obtain $\Var(r_x[0])$ we notice that the $\Var(r_x[m])$ is contained (for $-LN \leq m \leq LN$) on the diagonal of the covariance matrix of $\vec{\hat{r}_x}$, which is denoted by $\mat{C}_{\hat{r}_x}$.

This covariance matrix is equal to
\begin{align*}
\mat{C}_{\hat{r}_x} &= E(\vec{\hat{r}}_x\vec{\hat{r}}_x^T) - E(\vec{\hat{r}}_x) E(\vec{\hat{r}}_x^T)\\
&= R^{\dagger}C_{\hat{r}_y}(R^{\dagger})^H.
\end{align*}

The elements of the covariance matrix $C_{\hat{r}_y}$ are derived in \cite{ariananda2012compressive} to equal:

\begin{align}
\Cov(r_{{y_i},y_j}, r_{{y_w},y_v}) &= \frac{\sigma_n^4} r_{c_i,c_w}[0]\overline{r}_{c_j,c_v}[0]\delta[q-k].
\end{align}

The threshold $\gamma$ can then be calculated as

\begin{align*}
\gamma &= \frac{E(T_1)}{Q^{-1}(1-p_{fa})\sqrt{\Var(T_2)}+E(T_2)}
\end{align*}

\subsection{Filtering}
To be able to detect in a certain frequency band the input signal should be filtered in some way. However if the input signal $x[n]$ is filtered, then the noise in that input signal is also filtered: noise samples may become correlated. \cite{zheng2009spectrum} proposes a prewhiting technique
that can be used if the filter applied to $x[n]$ is known. In our case the detector is provided with $r_x[n]$ and no filter is applied to $x[n]$. 
We therefore, cannot use the prewhitening technique. 

% To determine the the threshold of the CAV detector we assume that the elements of the reconstructed auto correlation  $\hat{r}_x[n]$ are approximately gaussian distributed (see \cite{zheng2009spectrum} \cite{ariananda2012compressive}).

% However, unlike \cite{zheng2009spectrum} we cannot use the expression 
\end{document}