%!TEX program = xelatex

\documentclass[a4paper, openany, oneside]{memoir}
\input{../../../includes/preamble.tex}
\addbibresource{../../../includes/bibliography.bib}

\title{Compressive Sensing - An Overview}

\author{W.P. Bruinsma \and R.P. Hes \and H.J.C. Kroep \and T.C. Leliveld \and W.M. Melching \and T.A. aan de Wiel}

\raggedbottom

\begin{document}
%\section{Ethical paragraph}
This chapter is concerned with the ethical aspect of our business plan. The development of our product, a toolkit that enables high performance wideband spectrum sensing, has several possible consequences. This ethical paragraph will first discuss some of those possible consequences, to continue with a description of our policy to address  those issues, and other issues that have to be addressed in a business plan. 

A first possible consequence of introducing our technique is a rapid acceleration of developments in Cognitive Radio which, eventually
may lead to a wide-spread use of Cognitive Radio networks. This in turn, may lead to an increase in interference of licensed user and therefore to decrease of performance experienced by those users.  Another possible consequence of our technique is related to its misuse:
as the technique allows for fast wideband spectrum sensing, it also allows for fast tracking of user signals. This tracking may be used to eavesdrop communication (one could think of military applications). 

We take an utilitarian point of view at the responsibility of application of this product: as we can not exactly foresee all possible applications, nor do we have the capability to influence this; we will only take responsibility for the product itself. We expect that telecom agencies will regulate wide-spread use of wideband spectrum sensing and therefore will represent the interests of for example telecom providers, civilians and the military. By adhering to the local legal requirements of telecommunications we epxect that misuse of our toolkit is reduced to a bare minimum, while maintaining a commercially viable situation for our company.
Environmental and safety issues are off less concern in our business plan as our company is targeted at developing and maintaining a software toolkit. It does not focus on the actual hardware on which it may be used, and therefore it does not need a production line which entails those problems. As our company can be regarded as a high tech company, our employees will have to be higly educated and posses highly specialised knowledge in the area of wideband spectrum sensing and high-performance software development. We therefore will not impose gender quota as this can conflict with the need to hire highly educated employees and may have severe consequences for the operation of the company. 


\end{document}
