%!TEX program = xelatex

\documentclass[a4paper, openany, oneside]{memoir}
\input{../../includes/preamble.tex}
\addbibresource{../../includes/bibliography.bib}

\title{An Extensible Toolkit for Real-Time High-Performance Wideband Spectrum Sensing}

\author{W.P. Bruinsma \and R.P. Hes \and H.J.C. Kroep \and T.C. Leliveld \and W.M. Melching \and T.A. aan de Wiel}

\raggedbottom

\begin{document}
\chapter{Project description} \label{cha:problem_statement}
\section{Problem statement}
%TODO: REVISE

We have seen that Cognitive Radio has been introduced to alleviate the problem of spectrum scarcity.
At the heart of the Cognitive Radio lies spectrum sensing. Namely, it is essential that Cognitive Radio's are able to sense a wide band of the spectrum to detect the presence of primary users. To minimise the interference with licensed users, it is essential that this sensing process is as fast and as efficient as possible. Since Cognitive Radio networks are still in a conceptual stage, the need for a set of tools that can be used to sense a wide band with high efficiency arises.

This leads us to our problem statement:
\begin{center}
\emph{``Can we develop a toolkit which enables real-time high-performance wideband sensing?''}
\end{center}

\section{Proposed solution}
The development of such a toolkit requires knowledge of algorithms that can be used to perform wideband spectrum sensing. Such algorithms do not only include compressive sensing, but also include detection algorithms that are used to detect the presence of users. Furthermore, to implement and effectively test those algorithms, it is necessary that they are implemented in a modular software environment. Furthermore, we require that our toolkit can be tested on a hardware platform. Based on the complexity of our solution, we decide to divide the design of our toolkit in two parts.

Part I of the thesis will provide a mathematical framework which solves the design problem at a theoretical level. The toolkit will be based upon this framework, whose implementation will be developed separately.

Part II of the thesis will discuss the design of a modular software architecture which implements the theoretical framework discussed in Part I. This software architecture will enable to test the solutions proposed by the theoretical framework on a hardware platform.


\end{document}
