%!TEX program = xelatex

\documentclass[a4paper, openany, oneside]{memoir}
\input{../../includes/preamble.tex}
\addbibresource{../../includes/bibliography.bib}

\title{Compressive Sensing - An Overview}

\author{W.P. Bruinsma \and R.P. Hes \and H.J.C. Kroep \and T.C. Leliveld \and W.M. Melching \and T.A. aan de Wiel}

\raggedbottom

\begin{document}
\chapter{Preface}
The past eight weeks have been interesting, to say the least. Being in the last year of the Bachelor phase of our studies, the only thing that separates us from our degree is the graduation project. For us this was a huge incentive to deliver, which we hope we did. 

We have tried to combine an extensive mathematical analysis, software development and hardware design in this project, so that we could apply almost every aspect of our education. The result is this thesis. Although it might seem a rather lengthy piece, we would like to encourage the reader to consider the extent of the covered subjects, as well as the amount of care with which it was put together.

It does not end there though. During the project we have also ventured out of our comfort zone and looked into the marketability of potential applications. We even touched upon the ethical implications of such applications. The subject of is not included in this work, but will be presented separately as part of a business plan. It has, however, definitely influenced the path we set for ourselves during the course of the project.

All in all, we think the project was an instructive experience and hope that the following text reflects that, or even inspires the reader to continue to work in our footsteps. 

\end{document}
