%!TEX program = xelatex

\documentclass[a4paper, openany, oneside]{memoir}
\input{../../../../includes/preamble.tex}
\addbibresource{../../../../includes/bibliography.bib}

\begin{document}

% - intro (done)
% - afweging methoden (done)
% - algoritme (done)
% - afleiding (done)
% - garantie full rank -> lags (in afleiding) (done)
% - implementatie (generate + estimation) (todo)
% - conclusion (todo)

\section{Introduction}
In the introduction, we argued that we want to avoid sampling at the Nyquist frequency. In the previous chapter, we introduced the concept of multi-coset sampling. Therefore, it would be nice if the cosets in multi-coset sampling could sample at sub-Nyquist frequencies. The samples obtained by these cosets could then be used to reconstruct the power spectral density of the sampled signal, which, once more, we argued to be important during detection.

This chapter introduces a method to reconstruct the power spectral density of a signal which is sampled at sub-Nyquist frequencies. Usually, sampling at sub-Nyquist frequencies causes aliasing, which means that the obtained signal is distorted. Our reconstruction method should be able to reconstruct the power spectral density of the signal in real-time, despite the fact that the sampled signal is aliased. We focus on an accessible, yet complete explanation of such a reconstruction method.

First of all, we will consider various methods which allow for reconstruction of the power spectral density of signals sampled at sub-Nyquist frequencies. We will then, based on considerations developed in the next paragraph, choose one of these methods. Next, we will discuss an algorithm based on this method. Afterwards, we will discuss some details which turn out to be essential when implementing the algorithm.


\section{Overview}
There are various methods to reconstruct the power spectral density of a signal. These methods can be roughly divided in two groups: methodes based on signal reconstruction, such as \cite{bayarkernel, candes2006robust, candes2007sparsity, candes2008introduction, kirolos2006analog, li2014gomp, polo2009compressive, pal2011coprime}, and methods which are not based on signal reconstruction, such as \cite{ariananda2011multicoset,ariananda2012compressive}.




Methods of the first group are based on the assumption that the signal is either sparse, or contains few frequencies%
\footnote{More specifically, methods of the first group are based on the assumption that the signal is sparse in a certain basis. Let $\vec{x}$ denote the signal sampled at the Nyquist-frequency. Also, let the matrix $\mat{\Phi}$ consist of rows of the identity matrix such that $\vec{y}=\mat{\Phi}\vec{x}$ represents the signal sampled at a sub-Nyquist frequency. If $\vec{x}$ is sparse in the basis $\mat{\Psi}$, then there exists a sparse vector $\vec{s}$ such that $\vec{x}=\mat{\Psi}\vec{s}$. Given $\vec{y}$, the original signal $\vec{x}$ can be obtained by finding the most sparse vector $\vec{\hat{s}}$ such that $\vec{y}=\mat{\Phi}\mat{\Psi}\vec{\hat{s}}$. Then $\vec{x} = \mat{\Psi}\vec{\hat{s}}$. This problem can be formulated as an $l_1$-optimisation problem. Since it is assumed that the signal contains few frequencies, $\mat{\Psi}$ is often chosen to be the discrete Fourier transform matrix.}%
. Based on this assumption, they try to recover the signal sampled at sub-Nyquist frequencies. This can be done by optimisation\footnote{If the signal is assumed to be sparse, then $l_1$-optimisation is often used. Such optimisation consists of minimising the $l_1$-norm of a vector, which is the sum of the absolute value of the elements of the vector.} or by various algorithms\footnote{If the signal is assumed to contain few frequencies, then the MUSIC algorithm can be used \cite{pal2011coprime}.}. There are a few problems with this approach. First, the assumption that the signal is either sparse or contains few frequencies may be not true in our case, since we did not restrict the signal which the application must be able to process. Second, solving an optimisation problem or making use of such an algorithm in real-time yields a computationally expensive and complex reconstruction method. In constrast, methods of the second group are not based on the assumption the the signal is either sparse or contains few frequencies. They do not aim to reconstruct the signal, but try to solely reconstruct the power spectrum density. This allows for a computationally less expensive and less complex reconstruction method, but which is sufficient for detection purposes

Based on the stated reasoning, we decide to discuss a reconstruction method based on the method discussed in \cite{ariananda2012compressive}.


\end{document}