%!TEX program = xelatex

\documentclass[a4paper, openany, oneside]{memoir}
\input{../../../includes/preamble.tex}
\addbibresource{../../../includes/bibliography.bib}

\title{Compressive Sensing - An Overview}

\author{W.P. Bruinsma \and R.P. Hes \and H.J.C. Kroep \and T.C. Leliveld \and W.M. Melching \and T.A. aan de Wiel}

\raggedbottom

\begin{document}
\chapter{Conclusion}
% Eind conclusie

% wat wilden we ? Een high performance toolkit 
% wat hebben we gezien?

Approximately two months went by, and this is wat is left: the conclusion of our final work. Despite the division of this work into two parts, we consider it of utmost importance to reflect upon those parts in one conclusion, as together, those two parts form our final product. 

The problem statement has been introduced \cref{cha:problem_statement}, and motivated the seperation into two parts. \cref{sec:theory-specs,sec:implementation-specs} have specified what this problem statement entails for both parts. We will discuss each part seperately and we will end with a general conclusion of this thesis.

\section{General conclusion}
We have seen how in \cref{prt:theory} a theoretical framework has been developed. Its performance has been evaluated in \cref{sec:results_theory} and from its discussion we conclude that it meets all its \emph{must-have} requirements. Subsequently, the implementation of this theoretical framework has been described implemented in \cref{prt:implementation} and has been evaluated in \cref{cha:performance}. Combined, this bring us to the conclusion that we have succesfully developed the wideband spectrum sensing toolkig as envisioned in \cref{cha:problem_statement}. However, at the same time we do realize that the toolkit is still open to further improvement through future work. This thesis therefore does not provide \emph{the} answer to high performance wideband spectrum sensing, leaving it as an active area of research. 

This thesis, be it a small step forward in the vast area of wideband spectrum sensing, has been a huge step step for us.% in both \textbf{robin jij bent hier goed in dit cliche af te maken?}.

\raggedleft -- The authors \qquad\qquad\qquad





\end{document}
